---
title: "GO_analysis_Resp"
output: html_document
date: '2022-03-01'
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(clusterProfiler)
library(org.Hs.eg.db)
library(data.table)
```

## Respiratory

#Albuterol_DB01001
Read in PathFX result file.

```{r}
DB01001 <- read.csv("/Users/rachelzhang/Downloads/Albuterol_DB01001.csv")
DB01001 <- as.data.frame(DB01001) %>% column_to_rownames("X")
colnames(DB01001)
DB01001
```

Filter for phenotypes involving keyword "breast".

```{r}
DB01001_assocBreastCancer <- DB01001[grep('[bB]reast', DB01001$phenotype), ]
DB01001_assocBreastCancer
```
Extract genes associated with those phenotypes.

```{r}
DB01001_assocBreastCancer_geneID <- as.data.frame(DB01001_assocBreastCancer$genes)
DB01001_assocBreastCancer_geneID <- c("ADM", "ADORA2B", "AGFG1", "AP2A1", "APOB", "BIN1", "CALCR", "CD4", "CGA", "CRH", "CTTN", "CYP3A4", "DAB2", "EGF", "EGFR", "FNBP1L", "GHRH", "GNAS", "GRB2", "HGS", "HIP1", "IGF2R", "LHB", "LHCGR", "PTH", "PTH1R", "PTHLH", "REPS1", "REPS2", "SH3GL2", "SH3KBP1", "SNX9", "SYNJ2", "TFRC", "TRIP10", "VIP", "WASL", "WNT5A", "NPS", "AVP", "AP2S1" )
```

Converting gene names to Entrez ID.

```{r}
hs <- org.Hs.eg.db
my.symbols <- DB01001_assocBreastCancer_geneID
geneLst <- select(hs, 
                  keys = my.symbols,
                  columns = c("ENTREZID", "SYMBOL"),
                  keytype = "SYMBOL")
geneLst <- geneLst$ENTREZID
geneLst
```

GO over-representation analysis using package clusterProfiler.

```{r}
go <- enrichGO(geneLst, OrgDb = "org.Hs.eg.db", keyType = "ENTREZID", ont = "ALL", readable = TRUE)
```

View GO result.

```{r}
head(go, 25) %>% dplyr::select(ID, Description, pvalue, p.adjust) %>% DT::datatable(elementId = "goEle")
```

Export GO result.

```{r}
DB01001_assocBreastCancer_GO <- as.data.frame(go@result)
DB01001_assocBreastCancer_GO

write.csv(DB01001_assocBreastCancer_GO, "DB01001_GO_v2.csv")
```

# Budesonide_DB01222
Read in PathFX result file.

```{r}
DB01222 <- read.csv("/Users/rachelzhang/Downloads/Budesonide_DB01222.csv")
DB01222 <- as.data.frame(DB01222) %>% column_to_rownames("X")
colnames(DB01222)
DB01222
```

Filter for phenotypes involving keyword "breast".

```{r}
DB01222_assocBreastCancer <- DB01222[grep('[bB]reast', DB01222$phenotype), ]
DB01222_assocBreastCancer
```

Extract genes associated with those phenotypes.

```{r}
DB01222_assocBreastCancer_geneID <- as.data.frame(DB01222_assocBreastCancer$genes)
colnames(DB01222_assocBreastCancer_geneID)[1] <- "gene"
geneID_01222 <- unique(DB01222_assocBreastCancer_geneID)
geneIDs_01222 <- unlist(strsplit(geneID_01222$gene, ","))
```

Converting gene names to Entrez ID.

```{r}
hs <- org.Hs.eg.db
my.symbols <- geneIDs_01222
geneLst_01222 <- select(hs, 
                  keys = my.symbols,
                  columns = c("ENTREZID", "SYMBOL"),
                  keytype = "SYMBOL")
geneLst_01222 <- geneLst_01222$ENTREZID
geneLst_01222
```

GO over-representation analysis using package clusterProfiler.

```{r}
go <- enrichGO(geneLst_01222, OrgDb = "org.Hs.eg.db", keyType = "ENTREZID", ont = "ALL", readable = TRUE)
```

View GO result.

```{r}
head(go, 25) %>% dplyr::select(ID, Description, pvalue, p.adjust) %>% DT::datatable(elementId = "goEle")
```
Export GO result.

```{r}
DB01222_assocBreastCancer_GO <- as.data.frame(go@result)
DB01222_assocBreastCancer_GO

write.csv(DB01222_assocBreastCancer_GO, "DB01222_GO.csv")
```

#Formoterol_DB00983
Read in PathFX result file.

```{r}
DB00983 <- read.csv("/Users/rachelzhang/Downloads/Formoterol_DB00983.csv")
DB00983 <- as.data.frame(DB00983) %>% column_to_rownames("X")
colnames(DB00983)
DB00983
```

Filter for phenotypes involving keyword "breast".

```{r}
DB00983_assocBreastCancer <- DB00983[grep('[bB]reast', DB00983$phenotype), ]
DB00983_assocBreastCancer
```
Extract genes associated with those phenotypes.

```{r}
DB00983_assocBreastCancer_geneID <- as.data.frame(DB00983_assocBreastCancer$genes)
DB00983_assocBreastCancer_geneID <- c("AP2S1", "APOB", "AVP", "NPS", "PTH", "WNT5A")
```

Converting gene names to Entrez ID.

```{r}
hs <- org.Hs.eg.db
my.symbols <- DB00983_assocBreastCancer_geneID
geneLst_00983 <- select(hs, 
                  keys = my.symbols,
                  columns = c("ENTREZID", "SYMBOL"),
                  keytype = "SYMBOL")
geneLst_00983 <- geneLst_00983$ENTREZID
geneLst_00983
```

GO over-representation analysis using package clusterProfiler.

```{r}
go <- enrichGO(geneLst_00983, OrgDb = "org.Hs.eg.db", keyType = "ENTREZID", ont = "ALL", readable = TRUE)
```

View GO result.

```{r}
head(go, 25) %>% dplyr::select(ID, Description, pvalue, p.adjust) %>% DT::datatable(elementId = "goEle")
```
Export GO result.

```{r}
DB00983_assocBreastCancer_GO <- as.data.frame(go@result)
DB00983_assocBreastCancer_GO

write.csv(DB00983_assocBreastCancer_GO, "DB00983_GO.csv")
```





